Quantifying unmet ICU beds in tertiary hospitals in urban India using Propensity

### 2022-11-06 manuscript.Rmd

Aim
----

Quantify the unmet need for ICU beds in tertiaty hospitals in urban India.

@@

Anonymization
-------------
Hospital identification number

@@

(a) Describe all statistical methods, including those used to control
for confounding
-->
Propensity score matching (PSM) is useful method for identifying and assembling a control group from within a data set where there is causality between the independent and dependent variables, and a randomized case-control (RCT) study to offset or balance this bias is impractical, immoral or otherwise improper.

>>>>

Aim
----
Quantify the unmet need for ICU beds in tertiaty hospitals in urban India.

@@

Anonymization
-------------

<!-- You don't have to include all this in the thesis or a paper, definitely enough if you only provide a brief summary or cite the information on GitHub -->
Hospital identification number

@@

(a) Describe all statistical methods, including those used to control
for confounding
-->

Propensity score matching (PSM) is useful method for identifying and assembling a control group from within a data set where there is causality between the independent and dependent variables, and a randomized case-control (RCT) study to offset or balance this bias is impractical, immoral or otherwise improper.
